\begin{thebibliography}{99}

\bibitem{c1} Tran, T. M., Bui, D. C., Nguyen, T. V., and Nguyen, K. (2024). Transformer-based Spatio-Temporal Unsupervised Traffic Anomaly Detection in Aerial Videos. \textit{IEEE Transactions on Circuits and Systems for Video Technology}, vol. 34, no. 9, pp. 8292--8309. DOI: 10.1109/TCSVT.2024.3376399. [Online]. Available: \url{https://ieeexplore.ieee.org/document/10466765/}.

\bibitem{c2} Tran, T. M., Vu, T. N., Nguyen, T. V., and Nguyen, K. (2023). UIT-ADrone: A Novel Drone Dataset for Traffic Anomaly Detection. \textit{IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing}, vol. 16, pp. 5590--5601. DOI: 10.1109/JSTARS.2023.3285905. [Online]. Available: \url{https://ieeexplore.ieee.org/abstract/document/10158513/}.

\bibitem{c3} Bertasius, G., Wang, H., and Torresani, L. (2021). Is Space-Time Attention All You Need for Video Understanding?. \textit{Proceedings of the International Conference on Machine Learning (ICML)}. [Online]. Available: \url{https://arxiv.org/abs/2102.05095}.

\bibitem{c4} Arnab, A., Dehghani, M., Peemen, G., Schmid, C., Zisserman, A., and Houlsby, M. (2021). ViViT: A Video Vision Transformer. \textit{Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV)}. [Online]. Available: \url{https://arxiv.org/abs/2103.15691}.

\bibitem{c5} Yuan, H., Cai, Z., Zhou, H., Wang, Y., and Chen, X. (2021). TransAnomaly: Video Anomaly Detection Using Video Vision Transformer. \textit{IEEE Access}. [Online]. Available: \url{https://ieeexplore.ieee.org/document/9525368}.

\bibitem{c6} Noghre, G. A., Pazho, A. D., and Tabkhi, H. (2024). Human-Centric Video Anomaly Detection Through Spatio-Temporal Pose Tokenization and Transformer. \textit{arXiv preprint}. [Online]. Available: \url{https://arxiv.org/abs/2408.15185}.

\bibitem{c7} Gao, A., and Liu, J. (2025). STEAD: Spatio-Temporal Efficient Anomaly Detection for Time and Compute Sensitive Applications. \textit{arXiv preprint}. [Online]. Available: \url{https://arxiv.org/abs/2503.07942}.

\bibitem{c8} Ahn, S., and Ko, K. (2022). Video Vision Transformer for Traffic Violation Detection. \textit{IEEE Access}. [Online]. Available: \url{https://ieeexplore.ieee.org/abstract/document/11020668}.

\bibitem{c9} Park, H., Noh, J., and Ham, B. (2020). Learning Memory-guided Normality for Anomaly Detection. \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}.

\bibitem{c10} Liu, W., Luo, W., Lian, D., and Gao, S. (2018). Future Frame Prediction for Anomaly Detection -- A New Baseline. \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}.

\bibitem{c11} Liu, Z., et al. (2022). Video Swin Transformer. \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}. [Online]. Available: \url{https://ieeexplore.ieee.org/abstract/document/9740525}.

\bibitem{c12} Wu, J., et al. (2022). Video Anomaly Detection via Transformer with Spatio-Temporal Context. \textit{Computer Vision -- ECCV 2022 Workshops}. [Online]. Available: \url{https://link.springer.com/chapter/10.1007/978-3-031-19818-2_38}.

\end{thebibliography}
